### 2016-12-07 R/ITHIM.Rmd
Created gbdList by state

>>>>

## GBD Estimates by State

```{r stateBurden, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = TRUE, warning = FALSE}

stateNameToAbbrev <- function( stateName ){
  stateAbbrevMatrix <- matrix(c("Alabama","AL","Alaska","AK","Arizona","AZ","Arkansas","AR","California","CA","Colorado","CO","Connecticut","CT","Delaware","DE","District of Columbia","DC","Florida","FL","Georgia","GA","Hawaii","HI","Idaho","ID","Illinois","IL","Indiana","IN","Iowa","IA","Kansas","KS","Kentucky","KY","Louisiana","LA","Maine","ME","Maryland","MD","Massachusetts","MA","Michigan","MI","Minnesota","MN","Mississippi","MS","Missouri","MO","Montana","MT","Nebraska","NE","Nevada","NV","New Hampshire","NH","New Jersey","NJ","New Mexico","NM","New York","NY","North Carolina","NC"," North Dakota","ND","Ohio","OH","Oklahoma","OK","Oregon","OR","Pennsylvania","PA","Rhode Island","RI","South Carolina","SC","South Dakota","SD","Tennessee","TN","Texas","TX","Utah","UT","Vermont","VT","Virginia","VA","Washington","WA","West Virginia","WV","Wisconsin","WI","Wyoming","WY"), byrow = TRUE, ncol = 2)

  stateAbbrev <- stateAbbrevMatrix[,2]
  names(stateAbbrev) <- as.character(stateAbbrevMatrix[,1])
  return(stateAbbrev[stateName])
}

gbdParse <- function(gbd){
  gbdListTemp <- split(gbd,gbd$disease)
  gbdListTemp[["CVD"]] <- data.frame(disease = "CVD", gbdListTemp$IHD[,c("sex",  "ageClass")], gbdListTemp$IHD[,c("dproj","yll","yld","daly")] + gbdListTemp$InflammatoryHD[,c("dproj","yll","yld","daly")] + gbdListTemp$HHD[,c("dproj","yll","yld","daly")])
  gbdListTemp2 <- lapply(gbdListTemp,function(x) split(x,as.factor(x$sex)))
  gbdListTemp2 <- lapply(gbdListTemp2, function(x) list(M=x$M,F=x$F))
  return(gbdListTemp2)
}

gbdRDS <-  readRDS(file = "./data/stateMetroBurdens2014.rds")
gbdRDS <- within(gbdRDS, state <- stateNameToAbbrev(state))
gbdByState <- split(gbdRDS,gbdRDS$state)
gbdList <- lapply(gbdByState, gbdParse)
